---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

**NOTE: This is a toy package created for expository purposes. It is not meant to actually be useful. If you want a package for factor handling, please see [forcats](https://cran.r-project.org/package=forcats).**


I'm trying to fix Error: 'rcmd_safe_env' is not an exported object from 'namespace:callr'

***Refresher:*** when a character is converted into a factor, levels are ordered by defaul unless specified. Levels are unique categorical values, therefore, if the vector has already unique categorical values, it does not need to be converted into a factor and can remain as character.
the two function i wrote will help you assess whether a vector should be character of factor, and to return a vector with unordered levels.



### foofactors

Factors are a very useful type of variable in R, but they can also drive you nuts. This package provides some helper functions for the care and feeding of factors.

### Installation

```{r installation, eval = FALSE}
devtools::install_github("jennybc/foofactors")
```
  
### Quick demo

Binding two factors via `fbind()`:

```{r}
library(foofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work. Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```

### as is levels

as is levels returns a factor with levels in their original order

Example:

```{r}
## regular factor
pollo <- c("rooster", "chicken", "hen")
factor(pollo)
## levels as is
as_is_levels<- function (x) {
                factor(x, levels= unique(x))}
  
as_is_levels(pollo)
```

### Character or factor
character or factor compares the lenght of levels with the leght of the factor, if equal, it suggest it should be character, if not, factor.

Example:

```{r}
### repeted levels
pollos<- c("gallo", "gallo", "pollito", "gallina", "pollito")
char_not_fact(pollos)

### unique levels
char_not_fact<- function (x) {f<- as_is_levels(x)
if (length(f)== length(unique(levels(f)))) {
  return("that should be character")}

else {return("it should be a factor")
}
}
pollo <- c("rooster", "chicken", "hen")
char_not_fact(pollo)
```








